Tables/Graphs for Article

### 2017-11-29 article submission/draft1.Rnw
added table of results from final model

Questions analyzed were restricted to those posted in English (\Sexpr{nrow(x)} questions, 97\% of the full data). The time until event variable used in survival analysis was defined as the time since posting until a question received its first answer. For questions that did not receive an answer by the download date, time until event values were defined as the time since posting to the time the data was downloaded. These questions were considered right-censored, meaning that exact answer times for these questions are greater than the times in the data (questions can still receive answers after the download date).

@@

  Of \Sexpr{nrow(x)} questions, \Sexpr{answered} (\Sexpr{percentans}}\%) received an answer by the download date. The shortest answer time was \Sexpr{shortest} hours. The longest was \Sexpr{longest} hours (\Sexpr{longest_d} days). Figure ~\ref{fig:answertimes} shows the distribution of answer times for all questions, grouped by whether or not the question received an answer.

@@

\begin{table}[ht]
\centering
\caption{Univariate analysis results for categorical predictors, ordered by increasing p-values} 
\begin{tabular}{|p{12cm}|p{2cm}|}
  \hline
 Predictor & p-value \\ 
  \hline \hline
  Device category & 0.00 \\
  \hline
  Whether or not the user had been a member for less than one day before the question was posted & 0.00 \\ 
  \hline
  Whether or not the question's title ended in a questionmark & 0.00 \\ 
  \hline
  Whether or not the question's text contained at least one end punctuation mark & 0.00 \\ 
  \hline
  Day of the week the question was posted & 0.00 \\ 
  \hline
  Whether or not the question's text is in all lower case & 0.00 \\ 
  \hline
  Whether or not the user made an effort to solve the problem on their own, prior to asking the question & 0.00 \\ 
  \hline
  Whether or not the user edited or added information to the question's text sometime after posting it & 0.00 \\
  \hline
  Whether or not the question's title contains terms considered to be frequently used among unanswered questions & 0.00 \\ 
  \hline
  Whether or not the question's title contains terms considered to be frequently used among unanswered questions & 0.00 \\ 
   \hline
\end{tabular}
\label{table:cresults}
\end{table}

@@

Average performance metrics for test and training sets, found in table c, were considerably low. However, metrics did not change substantially from training to test sets, indicating that the model does not overfit. The following restricted cubic splines were applied continuous variables:

Results of cross-validation for the model including splines are in table d. As refitting the model without insignificant predictors and reperforming cross-validation did not change predictive accuracy, all variables were included. The final model, with all variables described above including splines, was fit to the full data.

@@

  To create these variables, the data was separated between answered and unanswered questions. Using text mining techniques, two lists were created-one for answered questions and another for unanswered questions--containing every word within the question's titles and the frequency or the number of time they occured among answered and unanswered questions. For ``frequently-used'' words in answered questions, that word would have to appear in more than 1\% of answered question's titles, and would have to appear in answered questions more than it appeared in unanswered questions. To determine the latter, a ratio of proportions was assessed. This ratio was calculated as the proportion of times a word occured among answered questions, to the proportion of times a word occured in unanswered questions. As an example, if ``cracked'' appeared in 2\% of answered questions and in 0.1\% of unanswered questions, it would be considered frequently used among answered questions as it occurs in more than 1\% of answered question's titles and occurs 20 times more in answered questions and in unanswered questions (ratio = 0.02/0.001 = 20). As for ``frequently-used'' words in unanswered questions, they must occur in 1\% or more of the question's titles and occur in more unanswered questions than unanswered questions (ratio < 1). Since there was some overlap between the words in each list and the device categories, every word that matched a device name was removed from the list. The resulting list for answered questions was 111 words, and 32 words in uanswered questions. Contain_answered and contain_unasnwered are logical variables, indicating true if a question's title contained at least one of the words in the frequently used words list for answered and unanswered questions, respectively.

@@

Title\_questionmark and title\_beginwh

These two variables were created to determine if stating the title in the form of a question is associated with faster answer times. Title_questionmark is a logical variable indicating true if the question's title ends with a question mark. Title_beginwh is a logical variable indicating true if the title begins with a “wh” word (e.g. "what", "when"). These variables were created based off of the findings from \citep{Bhat2014}.

@@

Ampm (change name)

The time of day the question was posted. If the question was posted between 5am and 12pm, it was categorized as ``morning''. If it was posted between 12pm and 5pm, it was categorized as ``afternoon'', between 5pm and 8am- ``evening'', and 8pm and 5 am, ``night''

>>>>

Questions analyzed were restricted to those posted in English. The time until event variable used in survival analysis was defined as the time since posting until a question received its first answer. For questions that did not receive an answer by the download date, time until event values were defined as the time since posting to the time the data was downloaded. These questions were considered right-censored, meaning that exact answer times for these questions are greater than the times in the data (questions can still receive answers after the download date).

@@

  Of 8,025 questions in the full data set, \Sexpr{nrow(x)} were in English (97\% of the full data). Of those questions, \Sexpr{answered} (\Sexpr{percentans}}\%) received an answer by the download date. The shortest answer time was \Sexpr{shortest} hours. The longest was \Sexpr{longest} hours (\Sexpr{longest_d} days). Figure ~\ref{fig:answertimes} shows the distribution of answer times for all questions, grouped by whether or not the question received an answer.

@@

\begin{table}[ht]
\centering
\caption{Univariate analysis results for categorical predictors, ordered by increasing p-values} 
\begin{tabular}{|p{12cm}|p{2cm}|}
  \hline
 Predictor & p-value \\ 
  \hline \hline
  Device category & 0.00 \\
  \hline
  Whether or not the user had been a member for less than one day before the question was posted & 0.00 \\ 
  \hline
  Whether or not the question's title ended in a questionmark & 0.00 \\ 
  \hline
  Whether or not the question's text contained at least one end punctuation mark & 0.00 \\ 
  \hline
  Day of the week the question was posted & 0.00 \\ 
  \hline
  Whether or not the question's text is in all lower case & 0.00 \\ 
  \hline
  Whether or not the user made an effort to solve the problem on their own, prior to asking the question & 0.00 \\ 
  \hline
  Whether or not the user edited or added information to the question's text sometime after posting it & 0.00 \\
  \hline
  Whether or not the question's title contains terms considered to be frequently used among unanswered questions & 0.00 \\ 
  \hline
  Whether or not the question's title contains terms considered to be frequently used among answered questions & 0.00 \\ 
   \hline
\end{tabular}
\label{table:cresults}
\end{table}

@@

\begin{table}[ht]
\centering
\caption{Average performance metrics for training and test sets} 
\begin{tabular}{rrrrrrrr}
  \hline
 & HR & LR & pval & R2 & AIC & Dxy & Concordance \\ 
  \hline
  Training Set & 2.00 & 959.49 & 0.00 & 0.14 & 64729.80 & 0.27 & 0.64 \\ 
  Test Set & 1.96 & 225.44 & 0.00 & 0.14 & 13453.18 & 0.26 & 0.63 \\ 
   \hline
\end{tabular}
\label{table:cv}
\end{table}

Average performance metrics for test and training sets, found in Table \ref{table:cv}, were considerably low. However, metrics did not change substantially from training to test sets, indicating that the model does not overfit. The final model, with all variables described above including splines, was fit to the full data.

\begin{table}[ht]
\centering
\caption{P-values for final model fit to the full data} 
\begin{tabular}{|p{12cm}|p{1cm}|}
  \hline
Predictor & p \\ 
  \hline \hline
Device Category & 0.00 \\ 
  \hline
Whether or not the user had been a member for less than one day before the question was posted & 0.00 \\ 
  \hline
Whether or not the question's title contains terms considered to be frequently used among unanswered questions & 0.00 \\
  \hline
Whether or not the question's title contains terms considered to be frequently used among answered questions & 0.22 \\ 
  \hline
Whether or not the question's title ended in a questionmark & 0.00 \\ 
  \hline
Whether or not the question's text contained at least one end punctuation mark & 0.53 \\ 
  \hline
Whether or not the question's text is in all lower case & 0.01 \\ 
  \hline
Whether or not the user edited or added information to the question's text sometime after posting it & 0.00 \\ 
  \hline
Whether or not the user made an effort to solve the problem on their own, prior to asking the question & 0.01 \\ 
  \hline
Day of the week the question was posted & 0.00 \\ 
  \hline
Square root transformation of the average frequency ``score'' of a question's tags & 0.00 \\ 
  \hline
Square root transformation of the average number of characters in a question's tags & 0.05 \\ 
Nonlinear & 0.08 \\ 
  \hline
Square root transformation of the number of characters in a question's text & 0.43 \\ 
Nonlinear & 0.46 \\ 
  \hline
Square root transformation of the number of characters in the user-defined device title & 0.28 \\ 
Nonlinear & 0.42 \\ 
  \hline
Square root transformation of the ratio of the number of line breaks to the number of characters in a question's text & 0.36 \\ 
Nonlinear & 0.62 \\ 
   \hline
\end{tabular}
\label{table:pvalues}
\end{table}

\begin{table}[ht]
\centering
\begin{tabular}{rlr}
  \hline
 & variable & coefficients \\ 
  \hline
1 & new\_category=Apple Product & 0.93 \\ 
  2 & new\_category=Camera & -0.26 \\ 
  3 & new\_category=Electronics & -0.08 \\ 
  4 & new\_category=Game Console & 0.21 \\ 
  5 & new\_category=Home & 0.39 \\ 
  6 & new\_category=Other & -0.11 \\ 
  7 & new\_category=PC & 0.43 \\ 
  8 & new\_category=Tablet & -0.15 \\ 
  9 & new\_category=Vehicle & 0.38 \\ 
  10 & new\_user=1 & -0.10 \\ 
  11 & contain\_unanswered & -0.27 \\ 
  12 & contain\_answered & 0.05 \\ 
  13 & title\_questionmark & 0.25 \\ 
  14 & text\_contain\_punct & 0.03 \\ 
  15 & text\_all\_lower & -0.18 \\ 
  16 & update & 0.28 \\ 
  17 & prior\_effort & -0.09 \\ 
  18 & weekday=Monday & 0.01 \\ 
  19 & weekday=Saturday & -0.07 \\ 
  20 & weekday=Sunday & -0.11 \\ 
  21 & weekday=Thursday & 0.03 \\ 
  22 & weekday=Tuesday & 0.09 \\ 
  23 & weekday=Wednesday & 0.10 \\ 
  24 & avg\_tag\_score & 2.23 \\ 
  25 & avg\_tag\_length & -0.08 \\ 
  26 & avg\_tag\_length' & 0.58 \\ 
  27 & avg\_tag\_length'' & -1.52 \\ 
  28 & text\_length & -0.08 \\ 
  29 & text\_length' & -0.36 \\ 
  30 & text\_length'' & 2.39 \\ 
  31 & text\_length''' & -3.69 \\ 
  32 & device\_length & -0.07 \\ 
  33 & device\_length' & 0.18 \\ 
  34 & device\_length'' & -0.27 \\ 
  35 & device\_length''' & 0.21 \\ 
  36 & newline\_ratio & 0.12 \\ 
  37 & newline\_ratio' & 0.36 \\ 
   \hline
\end{tabular}
\caption{Coefficients for predictors in the final model} 
\label{table:coefficients}
\end{table}

@@

  To create these variables, the data was separated between answered and unanswered questions. Using text mining techniques, two lists were created-one for answered questions and another for unanswered questions--containing every word within the question's titles and the frequency or the number of time they occured among answered and unanswered questions. For ``frequently-used'' words in answered questions, that word would have to appear in more than 1\% of answered question's titles, and would have to appear in answered questions more than it appeared in unanswered questions. To determine the latter, a ratio of proportions was assessed. This ratio was calculated as the proportion of times a word occured among answered questions, to the proportion of times a word occured in unanswered questions. As an example, if ``cracked'' appeared in 2\% of answered questions and in 0.1\% of unanswered questions, it would be considered frequently used among answered questions as it occurs in more than 1\% of answered question's titles and occurs 20 times more in answered questions and in unanswered questions (ratio = 0.02/0.001 = 20). As for ``frequently-used'' words in unanswered questions, they must occur in 1\% or more of the question's titles and occur in more unanswered questions than unanswered questions (ratio < 1). Since there was some overlap between the words in each list and the device categories, every word that matched a device name was removed from the list. The resulting list for answered questions was 111 words, and 32 words in uanswered questions. Contain\_answered and contain\_unasnwered are logical variables, indicating true if a question's title contained at least one of the words in the frequently used words list for answered and unanswered questions, respectively.

@@

@@

### 2017-11-29 article submission/draft1.tex
added table of results from final model

Questions analyzed were restricted to those posted in English (7760 questions, 97\% of the full data). The time until event variable used in survival analysis was defined as the time since posting until a question received its first answer. For questions that did not receive an answer by the download date, time until event values were defined as the time since posting to the time the data was downloaded. These questions were considered right-censored, meaning that exact answer times for these questions are greater than the times in the data (questions can still receive answers after the download date).

@@

  Of 7760 questions, 4951 (63.8}\%) received an answer by the download date. The shortest answer time was 0.5 hours. The longest was 2159.02 hours (89.96 days). Figure ~\ref{fig:answertimes} shows the distribution of answer times for all questions, grouped by whether or not the question received an answer.

>>>>

Questions analyzed were restricted to those posted in English. The time until event variable used in survival analysis was defined as the time since posting until a question received its first answer. For questions that did not receive an answer by the download date, time until event values were defined as the time since posting to the time the data was downloaded. These questions were considered right-censored, meaning that exact answer times for these questions are greater than the times in the data (questions can still receive answers after the download date).

@@

  Of 8,025 questions in the full data set, 7760 were in English (97\% of the full data). Of those questions, 4951 (63.8}\%) received an answer by the download date. The shortest answer time was 0.5 hours. The longest was 2159.02 hours (89.96 days). Figure ~\ref{fig:answertimes} shows the distribution of answer times for all questions, grouped by whether or not the question received an answer.

### 2017-11-29 article submission/graphics.Rmd
added table of results from final model

```{r}
model <- rms::cph(Surv(time_until_answer, answered) ~ new_category + new_user + 
                   contain_unanswered + contain_answered + title_questionmark + 
                   text_contain_punct + text_all_lower + update + prior_effort + weekday +
                   sqrt(avg_tag_score) + rcs(sqrt(avg_tag_length), 3) + rcs(log10(text_length), 3) +
                   rcs(sqrt(device_length), 4) + rcs(sqrt(newline_ratio), 3), 
                   data = x, 
                   x = TRUE, y = TRUE, 
                   surv = TRUE)
model
```

@@

@@

  # returns data frame with train/test metrics 
  statistics <- rbind(train_metrics, test_metrics)
  rownames(statistics) <- c("Training Data", "Test Data")
  return(statistics)
}

# function to average performance metrics, takes list of output from crossval
get_avgmetrics <- function(list) {
  avg <- rbind(train_avg = colMeans(purrr::map_df(1:length(list), ~rbind(list[[.]][1,]))), test_avg = colMeans(purrr::map_df(1:length(list), ~rbind(list[[.]][2,]))))
  return(avg)
}

# ------------------------------------------
# without splines
vars <- "new_category + new_user + contain_unanswered + contain_answered + title_questionmark + text_contain_punct + text_all_lower + update + prior_effort + weekday + sqrt(avg_tag_score) + text_length + device_length + sqrt(avg_tag_length) + newline_ratio"

cv_results <- purrr::map2(trains, tests, ~crossval(vars, .x, .y))
avg_results <- get_avgmetrics(cv_results)
avg_results

# ------------------------------------------
# with splines
vars1 <- "new_category + new_user + contain_unanswered + contain_answered + title_questionmark + text_contain_punct + text_all_lower + update + prior_effort + weekday + sqrt(avg_tag_score) + rcs(log10(text_length), 3) + rcs(sqrt(avg_tag_length), 3) + rcs(sqrt(device_length), 4) + rcs(sqrt(newline_ratio), 3)"

cv_results1 <- purrr::map2(trains, tests, ~crossval(vars1, .x, .y))
avg_results1 <- get_avgmetrics(cv_results1)
avg_results1
```

```{r}
avg_results1
```

@@

# final model on full data (table 5)

```{r}
# model statistics + parameters
# figure out how to get p-values 
parameterdf <- data.frame(variable = names(model$coefficients),
                          coefficients = round(unname(model$coefficients), 3))
parameterdf

modelstats <- data.frame(statistic = names(model$stats), 
                         value = round(unname(model$stats), 3))
modelstats

```{r}
final_metrics
```

>>>>

```{r}
model <- rms::cph(Surv(time_until_answer, answered) ~ new_category + new_user + 
                   contain_unanswered + contain_answered + title_questionmark + 
                   text_contain_punct + text_all_lower + update + prior_effort + weekday +
                   sqrt(avg_tag_score) + rcs(sqrt(avg_tag_length), 4) + rcs(log10(text_length), 5) +
                   rcs(sqrt(device_length), 5) + rcs(sqrt(newline_ratio), 3), 
                   data = x, 
                   x = TRUE, y = TRUE, 
                   surv = TRUE)
```

@@

trains <- list(train1, train2, train3, train4, train5)
trains <- purrr::map(trains, ~as.data.frame(.))
tests <- list(test1, test2, test3, test4, test5)
tests <- purrr::map(tests, ~as.data.frame(.))

@@

  # returns data frame with train/test metrics 
  statistics <- rbind(train_metrics, test_metrics)
  rownames(statistics) <- c("Training Data", "Test Data")
  return(statistics)
}
# ------------------------------------------
# function to average performance metrics, takes list of output from crossval
get_avgmetrics <- function(list) {
  avg <- rbind(train_avg = colMeans(purrr::map_df(1:length(list), ~rbind(list[[.]][1,]))), test_avg = colMeans(purrr::map_df(1:length(list), ~rbind(list[[.]][2,]))))
  return(avg)
}
# ------------------------------------------

vars1 <- "new_category + new_user + contain_unanswered + contain_answered + title_questionmark + text_contain_punct + text_all_lower + update + prior_effort + weekday + sqrt(avg_tag_score) + rcs(log10(text_length), 5) + rcs(sqrt(avg_tag_length), 4) + rcs(sqrt(device_length), 5) + rcs(sqrt(newline_ratio), 3)"

cv_results1 <- purrr::map2(trains, tests, ~crossval(vars1, .x, .y))
avg_results1 <- get_avgmetrics(cv_results1)
avg_results1
xtable::xtable(avg_results1, caption = "Average performance metrics for training and test sets", label = "table:cv")
```

# final model on full data

```{r}
# model statistics + parameters
# figure out how to get p-values 
parameterdf <- data.frame(variable = names(model$coefficients),
                          coefficients = round(unname(model$coefficients), 3))
parameterdf
xtable::xtable(parameterdf, caption = "Coefficients for predictors in the final model",
               label = "table:coefficients")
# ------------------------------------------
pvalues <- as.matrix(anova(model))[,3]
pvaluedf <- data.frame(variable = names(pvalues), 
                       pvalue = unname(pvalues))
xtable::xtable(pvaluedf, caption = "P-values for final model fit to the full data",
               label = "table:pvalues")

modelstats <- data.frame(statistic = names(model$stats), 
                         value = round(unname(model$stats), 3))
modelstats
# ------------------------------------------

```{r}
final_metrics
pvalues
anova(model)
```

@@
